Destruction of metrizability in generalized inverse limits

### 2015-11-04 articles/destroying-metrizability-in-generalized-inverse-limits/article.tex
final draft of preprint

\bibitem{varagona} Scott Varagona, {\it Generalized Inverse Limits Indexed by Totally Ordered Sets}, preprint (submitted to Topology Proceedings), 2015.

>>>>

\bibitem{varagona} Scott Varagona, {\it Generalized Inverse Limits Indexed by Totally Ordered Sets}, preprint (2015). Available at http://arxiv.org/abs/1511.00266
